---
title: "Tail_twist_0wpa"
author: "Tobias Gerber"
date: "7/22/2020"
output: html_document
---

mapping 

```{bash}
STAR --genomeDir /mnt/SingleCellGenomics/genome_data/STAR_AxolotlGenome/AmexG_v6_chr_unscaffolded/ --readFilesIn ./123454/raw/123454_S3_L001_R2_001.fastq.gz,./123454/raw/123454_S3_L002_R2_001.fastq.gz ./123454/raw/123454_S3_L001_R1_001.fastq.gz,./123454/raw/123454_S3_L002_R1_001.fastq.gz --soloType CB_UMI_Simple --soloCBwhitelist ~/cellranger-3.1.0/cellranger-cs/3.1.0/lib/python/cellranger/barcodes/3M-february-2018.txt --soloCBmatchWLtype 1MM_multi_Nbase_pseudocounts --soloUMIfiltering MultiGeneUMI_CR --soloUMIdedup 1MM_CR --readFilesCommand zcat --outFileNamePrefix count_123454_0dpa_twist3_Full_ --runThreadN 45 --soloMultiMappers Uniform --soloCellFilter EmptyDrops_CR --soloCBstart 1  --soloCBlen 16  --soloUMIstart 17  --soloUMIlen 12 --soloFeatures Gene GeneFull Velocyto --outSAMtype BAM Unsorted --soloBarcodeReadLength 0
```


```{r setup, include=FALSE}

#Load libraries

library(Seurat)
library(dplyr)
library(Matrix)
library(RColorBrewer)

```

##Load Data
```{r}

setwd("~/Projects/SingleCellGroup/Axolotl/Tail_Project_0wpa_twist/")


#load annotation file

anno = read.delim("/mnt/SingleCellGenomics/genome_data/10xAxolotlGenome/AnnotationFile_AmexG_v6_chr_unscaffolded_CherryGFP_v1.2.csv",sep = ";",header = F)
rownames(anno) = anno[,1]


############# remove weird transposon / unannotated genes
unannotated.transcripts = rownames(anno)[anno$V2 %in% anno$V2[grep("PEG10",anno$V2)] ]
unannotated.transcripts = unique(c(rownames(anno)[anno$V2 %in% anno$V2[grep("L1TD1",anno$V2)] ], unannotated.transcripts))
unannotated.transcripts = unique(c(rownames(anno)[anno$V2 %in% anno$V2[grep("RTL",anno$V2)] ], unannotated.transcripts))
unannotated.transcripts = unique(c(rownames(anno)[anno$V2 %in% anno$V2[grep("GIN1",anno$V2)] ], unannotated.transcripts))
unannotated.transcripts = unique(c(rownames(anno)[anno$V2 %in% anno$V2[grep("L1\\-RT",anno$V2)] ], unannotated.transcripts))
unannotated.transcripts = unique(c(rownames(anno)[anno$V2 %in% anno$V2[grep("^N\\/A",anno$V2)] ], unannotated.transcripts))
#unannotated.transcripts = unique(c(rownames(anno)[anno$V2 %in% anno$V2[grep("^AMEX",anno$V2)] ], unannotated.transcripts))

anno = anno[!rownames(anno) %in% unannotated.transcripts,]


############# remove rp genes

rp.genes_AmexG = rownames(anno)[anno$V2 %in% anno$V2[grep("RPL",anno$V2)]]
rp.genes_AmexG = unique(c(rownames(anno)[anno$V2 %in% anno$V2[grep("RPS",anno$V2)] ], rp.genes_AmexG))

anno = anno[!rownames(anno) %in% rp.genes_AmexG,]


library(tidyverse)

############# get data and remove genes

Tail_twist_0wpa <- Read10X(data.dir = "/mnt/SingleCellGenomics/scg_projects/10xGenomics/HLFYTDRXX_R9843/count_123454_0dpa_twist3_Full_Solo.out/Gene/raw/")

Tail_twist_0wpa = Tail_twist_0wpa[rownames(anno), ,drop = FALSE]

library(dplyr)
library(Seurat)

############# load in Seurat

Tail_twist_0wpa <- CreateSeuratObject(counts = Tail_twist_0wpa, project = "Tail_twist_0wpa", min.cells = 3, min.features = 200)
Tail_twist_0wpa


```


##Run Seurat

###All cells

```{r}
mito.genes <- c("ND2","ND1","ND3","ND4","ND4L","ND5","ND6")
mito.contig <- intersect(c(rownames(anno)[anno$V2 %in% mito.genes ] , rownames(anno)[anno$V2 %in% anno$V2[grep("^COX",anno$V2)]] ) , rownames(Tail_twist_0wpa))


Tail_twist_0wpa[["percent.mt"]] <- PercentageFeatureSet(Tail_twist_0wpa, features = mito.contig)


#parallize scaling
library(future)
plan("multiprocess", workers = 8)
plan()

#set maximum to 50GB for each worker
options(future.globals.maxSize = 50000 * 1024^2)

#normalize data

Tail_twist_0wpa = NormalizeData(Tail_twist_0wpa)

plot1 <- FeatureScatter(Tail_twist_0wpa, feature1 = "nCount_RNA", feature2 = "percent.mt")
plot2 <- FeatureScatter(Tail_twist_0wpa, feature1 = "nCount_RNA", feature2 = "nFeature_RNA")


pdf("./Tail_twist_0wpa_QC_PreFilter.pdf",width=10,height=5)
VlnPlot(Tail_twist_0wpa, features = c("nCount_RNA","nFeature_RNA","percent.mt"),pt.size = -1)
CombinePlots(plots = list(plot1, plot2))
dev.off()

Tail_twist_0wpa <- subset(Tail_twist_0wpa, subset = nCount_RNA < 10000  & nCount_RNA > 1000  & percent.mt < 15 )

plot1 <- FeatureScatter(Tail_twist_0wpa, feature1 = "nCount_RNA", feature2 = "percent.mt")
plot2 <- FeatureScatter(Tail_twist_0wpa, feature1 = "nCount_RNA", feature2 = "nFeature_RNA")


pdf("./Tail_twist_0wpa_QC_PostFilter.pdf",width=10,height=5)
VlnPlot(Tail_twist_0wpa, features = c("nCount_RNA","nFeature_RNA","percent.mt"),pt.size = -1)
CombinePlots(plots = list(plot1, plot2))
dev.off()


#get cell cycle genes

g2m.genes <- cc.genes$g2m.genes
g2m.contig <- intersect(rownames(anno)[anno$V2 %in% g2m.genes ] , rownames(Tail_twist_0wpa) )

s.genes <- cc.genes$s.genes
s.contig <- intersect(rownames(anno)[anno$V2 %in% s.genes ] , rownames(Tail_twist_0wpa) )

#cell cycle scoring
Tail_twist_0wpa <- CellCycleScoring(Tail_twist_0wpa, s.features = s.contig, g2m.features = g2m.contig, set.ident = TRUE)


#scale
#ScaleData(  object,  features = NULL,  assay = NULL,  vars.to.regress = NULL,  split.by = NULL,  model.use = "linear",  use.umi = FALSE,  do.scale = TRUE,  do.center = TRUE,  scale.max = 10,  block.size = 1000,  min.cells.to.block = 3000,  verbose = TRUE)

all.genes <- rownames(Tail_twist_0wpa)

Tail_twist_0wpa = ScaleData(  Tail_twist_0wpa, features = all.genes ,vars.to.regress = c("nCount_RNA","percent.mt"))

#run PCA on all genes
#RunPCA(object, assay = NULL, features = NULL,  npcs = 50, rev.pca = FALSE, weight.by.var = TRUE, verbose = TRUE,  ndims.print = 1:5, nfeatures.print = 30, reduction.name = "pca",  reduction.key = "PC_", seed.use = 42)

all.genes.noFluo = all.genes[!all.genes %in% c("eGFP","mCherry")]

Tail_twist_0wpa = RunPCA(Tail_twist_0wpa,features = all.genes.noFluo,npcs = 100)

#plot PCA heatmaps
#DimHeatmap(pbmc, dims = 1, cells = 500, balanced = TRUE)

library(RColorBrewer)

pdf("Tail_twist_0wpa_PCAheatmaps.pdf",width=30,height=20)
DimHeatmap(Tail_twist_0wpa, dims = 1:16, cells = 1000, balanced = TRUE, ncol = 4,  fast = F) 
DimHeatmap(Tail_twist_0wpa, dims = 17:32, cells = 1000, balanced = TRUE, ncol = 4,  fast = F) 
DimHeatmap(Tail_twist_0wpa, dims = 33:48, cells = 1000, balanced = TRUE,  ncol = 4, fast = F) 
DimHeatmap(Tail_twist_0wpa, dims = 49:64, cells = 1000, balanced = TRUE,  ncol = 4, fast = F) 
DimHeatmap(Tail_twist_0wpa, dims = 65:80, cells = 1000, balanced = TRUE,  ncol = 4, fast = F) 
DimHeatmap(Tail_twist_0wpa, dims = 81:96, cells = 1000, balanced = TRUE,  ncol = 4, fast = F) 
dev.off()

#elbow plot
pdf("Tail_twist_0wpa_PCelbow.pdf",width=20,height=10)
ElbowPlot(Tail_twist_0wpa, ndims = 100)
dev.off()

#Cluster cells
Tail_twist_0wpa<- FindNeighbors(Tail_twist_0wpa, dims = 1:30)
Tail_twist_0wpa <- FindClusters(Tail_twist_0wpa, resolution = 0.4)

#run UMAP
Tail_twist_0wpa = RunUMAP(Tail_twist_0wpa,dims = 1:30)


#plot result
#DimPlot(object, dims = c(1, 2), cells = NULL, cols = NULL,  pt.size = NULL, reduction = NULL, group.by = NULL,  split.by = NULL, shape.by = NULL, order = NULL, label = FALSE,  label.size = 4, repel = FALSE, cells.highlight = NULL,  cols.highlight = "red", sizes.highlight = 1, na.value = "grey50",  combine = TRUE)

pdf("Tail_twist_0wpa_UMAP_PC30_res0.4.pdf",width=10,height=10)
DimPlot(object = Tail_twist_0wpa, reduction = 'umap', pt.size = 2)
FeaturePlot(Tail_twist_0wpa, pt.size = 0.5, features = c("nFeature_RNA","nCount_RNA","percent.mt","mCherry","eGFP"),order = T, cols = c(brewer.pal(9,"Greys")[9:2],brewer.pal(9,"Reds")[2:9]))
dev.off()


plan("multiprocess", workers = 8)
library(tidyverse)

markers <- FindAllMarkers(Tail_twist_0wpa, only.pos = TRUE,  logfc.threshold = 0.3)
markers.anno = markers
markers.anno = merge(markers.anno,anno, by.x="gene" , by.y="V1")
markers.anno$ID = markers.anno$gene

#markers.anno = markers.anno[order(as.numeric(markers.anno$cluster)),]
markers.anno = markers.anno  %>% arrange(cluster , desc(avg_log2FC))

write.csv(markers.anno,"Tail_twist_0wpa_allMarker.csv")

#c10 epidermis
#c11 blood
#c3/4/8/9 macrophages



saveRDS(Tail_twist_0wpa, file = "Tail_twist_0wpa_SeuratObj.RDS")

```

COL6A1	AMEX60DD055540
TWIST3-TWIST2	AMEX60DD029436
TNMD	AMEX60DD037674
ASPN	AMEX60DD023964
MEOX1	AMEX60DD009987
MGP	AMEX60DD030520
CNMD	AMEX60DD048972
OTOS	AMEX60DD002658
GREM1	AMEX60DD012132
PRRX1	AMEX60DD018450
MYH11	AMEX60DD020580
ACTA2	AMEX60DD052517
TAGLN	AMEX60DD053922
COL8A1	AMEX60DD048332
MATN3	AMEX60DD033105
C1QB	AMEX60DD052070
LGALS3BP	AMEX60DD031414
PLBD1	AMEX60DD029125
LECT2	AMEX60DD024964
S100P	AMEX60DD045921
EPCAM	AMEX60DD035908
VWF	AMEX60DD006619
PLVAP	AMEX60DD013910


AMEX60DD018450    PRRX1
AMEX60DD009987    MEOX1	
AMEX60DD022442    MEOX2	
AMEX60DD040818    SCX
AMEX60DD037674    TNMD
AMEX60DD052322    PAX7
AMEX60DD042540    MEF2C
AMEX60DD007644    MYF5
AMEX60DD055512    TWIST2
AMEX60DD029436    TWIST3
AMEX60DD031236    SOX9
AMEX60DD002658    OTOS
AMEX60DD037123    CHRDL1
AMEX60DD036008    PKDCC
AMEX60DD004178    ACAN
AMEX60DD048972    CNMD
AMEX60DD029426	COL2A1

####Plot Marker

```{r}
#plot markers

library(RColorBrewer)
library(viridis)

gene_ids = c("AMEX60DD055540","AMEX60DD029436","AMEX60DD037674","AMEX60DD023964","AMEX60DD009987","AMEX60DD030520","AMEX60DD048972","AMEX60DD002658","AMEX60DD012132","AMEX60DD018450","AMEX60DD020580","AMEX60DD052517","AMEX60DD053922","AMEX60DD048332","AMEX60DD033105","AMEX60DD052070","AMEX60DD031414","AMEX60DD029125","AMEX60DD024964","AMEX60DD045921","AMEX60DD035908","AMEX60DD006619","AMEX60DD013910","AMEX60DD012191","AMEX60DD041421","AMEX60DD027586","AMEX60DD001756","AMEX60DD055612")

gene_names =c("COL6A1","TWIST3-TWIST2","TNMD","ASPN","MEOX1","MGP","CNMD","OTOS","GREM1","PRRX1","MYH11","ACTA2","TAGLN","COL8A1","MATN3","C1QB","LGALS3BP","PLBD1","LECT2","S100P","EPCAM","VWF","PLVAP","COCH","MSMP","SULF2","MECOM","HOXD13")

gg_Fig <- FeaturePlot(Tail_twist_0wpa, pt.size = 0.5, features = gene_ids,order = T, cols = c("grey",rev(viridis_pal(option = "viridis")(12))), repel=T)
gg_Fig <- lapply( 1:length(gene_ids), function(x) { gg_Fig[[x]] + labs(title=gene_names[x]) & NoLegend() & NoAxes()})

pdf("Tail_twist_0wpa_UMAP_feature_GeneralCellTypeMarker.pdf",width=13,height=10)
CombinePlots( gg_Fig )
dev.off()
	

library(viridis)

gene_ids = c("AMEX60DD018450","AMEX60DD034707","AMEX60DD052891","AMEX60DD033766","AMEX60DD021249","AMEX60DD027155","AMEX60DD009987","AMEX60DD022442","AMEX60DD040818","AMEX60DD037674","AMEX60DD052322","AMEX60DD007644","AMEX60DD055512","AMEX60DD029436","AMEX60DD031236","AMEX60DD002658","AMEX60DD037123","AMEX60DD036008","AMEX60DD004178","AMEX60DD048972","AMEX60DD029426","eGFP","mCherry","AMEX60DD054775")
	
gene_names =c("PRRX1","RSPO3","FGF8","TBX18","UNCX","TCF15","MEOX1","MEOX2","SCX","TNMD","PAX7","MYF5","TWIST2","TWIST3","SOX9","OTOS","CHRDL1","PKDCC","ACAN","CNMD","COL2A1","eGFP","mCherry","CALYMMIN")

gg_Fig <- FeaturePlot(Tail_twist_0wpa, pt.size = 0.2, features = gene_ids,order = T, cols = c("grey",rev(viridis_pal(option = "viridis")(12))), repel=T)
gg_Fig <- lapply( 1:length(gene_ids), function(x) { gg_Fig[[x]] + labs(title=gene_names[x]) & NoLegend() & NoAxes()})

pdf("Tail_twist_0wpa_UMAP_feature_ABMarker.pdf",width=15,height=10)
CombinePlots( gg_Fig )
dev.off()


```

### CT

```{r}
######select clean CT population

Tail_twist_0wpa_CT <- subset(Tail_twist_0wpa, idents = c(0,1,2,5,6,7) )

#renormalize andf scale

Tail_twist_0wpa_CT = NormalizeData(Tail_twist_0wpa_CT)


all.genes <- rownames(Tail_twist_0wpa_CT)

Tail_twist_0wpa_CT = ScaleData(  Tail_twist_0wpa_CT, features = all.genes ,vars.to.regress = c("nCount_RNA","percent.mt"))

#run PCA on all genes
#RunPCA(object, assay = NULL, features = NULL,  npcs = 50, rev.pca = FALSE, weight.by.var = TRUE, verbose = TRUE,  ndims.print = 1:5, nfeatures.print = 30, reduction.name = "pca",  reduction.key = "PC_", seed.use = 42)

all.genes.noFluo = all.genes[!all.genes %in% c("eGFP","mCherry")]

Tail_twist_0wpa_CT = RunPCA(Tail_twist_0wpa_CT,features = all.genes.noFluo,npcs = 100)


#Recluster cells to get a clean population
Tail_twist_0wpa_CT<- FindNeighbors(Tail_twist_0wpa_CT, dims = 1:50)
Tail_twist_0wpa_CT <- FindClusters(Tail_twist_0wpa_CT, resolution = 0.8)

#run UMAP
Tail_twist_0wpa_CT = RunUMAP(Tail_twist_0wpa_CT,dims = 1:50,min.dist = 0.001)

#plot result
#DimPlot(object, dims = c(1, 2), cells = NULL, cols = NULL,  pt.size = NULL, reduction = NULL, group.by = NULL,  split.by = NULL, shape.by = NULL, order = NULL, label = FALSE,  label.size = 4, repel = FALSE, cells.highlight = NULL,  cols.highlight = "red", sizes.highlight = 1, na.value = "grey50",  combine = TRUE)

pdf("Tail_twist_0wpa_CT_UMAP_PC50_res0.8.pdf",width=10,height=10)
DimPlot(object = Tail_twist_0wpa_CT, reduction = 'umap', shuffle = T, pt.size = 2)
FeaturePlot(Tail_twist_0wpa_CT, pt.size = 2, features = c("nCount_RNA","G2M.Score","eGFP","mCherry"),order = T,raster = T, cols = c("grey",rev(viridis_pal(option = "viridis")(12))))
dev.off()

plan("multiprocess", workers = 8)
library(tidyverse)

markers <- FindAllMarkers(Tail_twist_0wpa_CT, only.pos = TRUE,  logfc.threshold = 0.3)
markers.anno = markers
markers.anno = merge(markers.anno,anno, by.x="gene" , by.y="V1")
markers.anno$ID = markers.anno$gene

#markers.anno = markers.anno[order(as.numeric(markers.anno$cluster)),]
markers.anno = markers.anno  %>% arrange(cluster , desc(avg_log2FC))

write.csv(markers.anno,"Tail_twist_0wpa_CT_allMarker.csv")


gene_ids = c("AMEX60DD018450","AMEX60DD034707","AMEX60DD052891","AMEX60DD033766","AMEX60DD021249","AMEX60DD027155","AMEX60DD009987","AMEX60DD022442","AMEX60DD040818","AMEX60DD037674","AMEX60DD052322","AMEX60DD007644","AMEX60DD055512","AMEX60DD029436","AMEX60DD031236","AMEX60DD002658","AMEX60DD037123","AMEX60DD036008","AMEX60DD004178","AMEX60DD048972","AMEX60DD029426","AMEX60DD007033","AMEX60DD009952","AMEX60DD023726","AMEX60DD034517","AMEX60DD043904","AMEX60DD009968","AMEX60DD038105","AMEX60DD027586","AMEX60DD054775")
	
gene_names =c("PRRX1","RSPO3","FGF8","TBX18","UNCX","TCF15","MEOX1","MEOX2","SCX","TNMD","PAX7","MYF5","TWIST2","TWIST3","SOX9","OTOS","CHRDL1","PKDCC","ACAN","CNMD","COL2A1","FAM180A","DLX3","WNT5A","DLL1","SPP1","PHOSPHO1","INHBA","SULF2","CALYMMIN")



gg_Fig <- FeaturePlot(Tail_twist_0wpa_CT, pt.size = 0.2, features = gene_ids,order = T, cols = c("grey",rev(viridis_pal(option = "viridis")(12))), repel=T)
gg_Fig <- lapply( 1:length(gene_ids), function(x) { gg_Fig[[x]] + labs(title=gene_names[x]) & NoLegend() & NoAxes()})

pdf("Tail_twist_0wpa_CT_UMAP_feature_ABMarker.pdf",width=13,height=10)
CombinePlots( gg_Fig )
dev.off()


gene_ids = c("AMEX60DD034517","AMEX60DD021181","AMEX60DD021249","AMEX60DD018450","AMEX60DD034707","AMEX60DD052891","AMEX60DD033766","AMEX60DD027155","AMEX60DD009987","AMEX60DD022442","AMEX60DD040818","AMEX60DD037674","AMEX60DD007644","AMEX60DD052322","AMEX60DD055512","AMEX60DD029436","AMEX60DD054625","AMEX60DD007033","AMEX60DD018705","AMEX60DD024616","AMEX60DD038300","AMEX60DD012132","AMEX60DD031236","AMEX60DD002658","AMEX60DD037123","AMEX60DD036008","AMEX60DD004178","AMEX60DD048972","AMEX60DD029426","AMEX60DD005459","AMEX60DD043904","AMEX60DD049488","AMEX60DD033105","AMEX60DD038318","AMEX60DD031842","AMEX60DD047873","AMEX60DD034687","AMEX60DD008143","AMEX60DD048840","AMEX60DD043904","AMEX60DD009968")
gene_names =c("DLL1","LFNG","UNCX","PRRX1","RSPO3","FGF8","TBX18","TCF15","MEOX1","MEOX2","SCX","TNMD","MYF5","PAX7","TWIST2","TWIST3","TBX2","FAM180A","F13B","LTBP4","F13A1","GREM1","SOX9","OTOS","CHRDL1","PKDCC","ACAN","CNMD","COL2A1","MATN1","SPP1","MMP13","MATN3","DSP","COL5A3","COL4A1","LAMA2","ITIH5","KLF5","SPP1","PHOSPHO1")
	

gg_Fig <- FeaturePlot(Tail_twist_0wpa_CT, pt.size = 2, features = gene_ids,order = T,raster = T, cols = c("grey",rev(viridis_pal(option = "viridis")(12))), repel=T)
gg_Fig <- lapply( 1:length(gene_ids), function(x) { gg_Fig[[x]] + labs(title=gene_names[x]) & NoLegend() & NoAxes()})

pdf("Tail_twist_0wpa_CT_UMAP_feature_TailRegMarker.pdf",width=13,height=10)
CombinePlots( gg_Fig )
dev.off()

#cluster 8 is macrophage

#cluster 6 is unclear

Tail_twist_0wpa_CT = subset(Tail_twist_0wpa_CT, idents = c(0,1,2,3,4,5,6,7,9))


#Recluster cells to get a clean population
Tail_twist_0wpa_CT<- FindNeighbors(Tail_twist_0wpa_CT, dims = 1:50)
Tail_twist_0wpa_CT <- FindClusters(Tail_twist_0wpa_CT, resolution = 0.8)

#run UMAP
Tail_twist_0wpa_CT = RunUMAP(Tail_twist_0wpa_CT,dims = 1:50,min.dist = 0.001)

#plot result
#DimPlot(object, dims = c(1, 2), cells = NULL, cols = NULL,  pt.size = NULL, reduction = NULL, group.by = NULL,  split.by = NULL, shape.by = NULL, order = NULL, label = FALSE,  label.size = 4, repel = FALSE, cells.highlight = NULL,  cols.highlight = "red", sizes.highlight = 1, na.value = "grey50",  combine = TRUE)

pdf("Tail_twist_0wpa_CT_UMAP_PC50_res0.8.pdf",width=10,height=10)
DimPlot(object = Tail_twist_0wpa_CT, reduction = 'umap', shuffle = T, pt.size = 2)
FeaturePlot(Tail_twist_0wpa_CT, pt.size = 2, features = c("nCount_RNA","G2M.Score","eGFP","mCherry"),order = T,raster = T, cols = c("grey",rev(viridis_pal(option = "viridis")(12))))
dev.off()

#no contamination clusters identified anymore

plan("multiprocess", workers = 8)
library(tidyverse)

markers <- FindAllMarkers(Tail_twist_0wpa_CT, only.pos = TRUE,  logfc.threshold = 0.3)
markers.anno = markers
markers.anno = merge(markers.anno,anno, by.x="gene" , by.y="V1")
markers.anno$ID = markers.anno$gene

#markers.anno = markers.anno[order(as.numeric(markers.anno$cluster)),]
markers.anno = markers.anno  %>% arrange(cluster , desc(avg_log2FC))

write.csv(markers.anno,"Tail_twist_0wpa_CT_allMarker.csv")


gene_ids = c("AMEX60DD018450","AMEX60DD034707","AMEX60DD052891","AMEX60DD033766","AMEX60DD021249","AMEX60DD027155","AMEX60DD009987","AMEX60DD022442","AMEX60DD040818","AMEX60DD037674","AMEX60DD052322","AMEX60DD007644","AMEX60DD055512","AMEX60DD029436","AMEX60DD031236","AMEX60DD002658","AMEX60DD037123","AMEX60DD036008","AMEX60DD004178","AMEX60DD048972","AMEX60DD029426","AMEX60DD007033","AMEX60DD009952","AMEX60DD023726","AMEX60DD034517","AMEX60DD043904","AMEX60DD009968","AMEX60DD038105","AMEX60DD027586","AMEX60DD054775")
	
gene_names =c("PRRX1","RSPO3","FGF8","TBX18","UNCX","TCF15","MEOX1","MEOX2","SCX","TNMD","PAX7","MYF5","TWIST2","TWIST3","SOX9","OTOS","CHRDL1","PKDCC","ACAN","CNMD","COL2A1","FAM180A","DLX3","WNT5A","DLL1","SPP1","PHOSPHO1","INHBA","SULF2","CALYMMIN")



gg_Fig <- FeaturePlot(Tail_twist_0wpa_CT, pt.size = 0.2, features = gene_ids,order = T, cols = c("grey",rev(viridis_pal(option = "viridis")(12))), repel=T)
gg_Fig <- lapply( 1:length(gene_ids), function(x) { gg_Fig[[x]] + labs(title=gene_names[x]) & NoLegend() & NoAxes()})

pdf("Tail_twist_0wpa_CT_UMAP_feature_ABMarker.pdf",width=13,height=10)
CombinePlots( gg_Fig )
dev.off()


gene_ids = c("AMEX60DD034517","AMEX60DD021181","AMEX60DD021249","AMEX60DD018450","AMEX60DD034707","AMEX60DD052891","AMEX60DD033766","AMEX60DD027155","AMEX60DD009987","AMEX60DD022442","AMEX60DD040818","AMEX60DD037674","AMEX60DD007644","AMEX60DD052322","AMEX60DD055512","AMEX60DD029436","AMEX60DD054625","AMEX60DD007033","AMEX60DD018705","AMEX60DD024616","AMEX60DD038300","AMEX60DD012132","AMEX60DD031236","AMEX60DD002658","AMEX60DD037123","AMEX60DD036008","AMEX60DD004178","AMEX60DD048972","AMEX60DD029426","AMEX60DD005459","AMEX60DD043904","AMEX60DD049488","AMEX60DD033105","AMEX60DD038318","AMEX60DD031842","AMEX60DD047873","AMEX60DD034687","AMEX60DD008143","AMEX60DD048840","AMEX60DD043904","AMEX60DD009968")
gene_names =c("DLL1","LFNG","UNCX","PRRX1","RSPO3","FGF8","TBX18","TCF15","MEOX1","MEOX2","SCX","TNMD","MYF5","PAX7","TWIST2","TWIST3","TBX2","FAM180A","F13B","LTBP4","F13A1","GREM1","SOX9","OTOS","CHRDL1","PKDCC","ACAN","CNMD","COL2A1","MATN1","SPP1","MMP13","MATN3","DSP","COL5A3","COL4A1","LAMA2","ITIH5","KLF5","SPP1","PHOSPHO1")
	

gg_Fig <- FeaturePlot(Tail_twist_0wpa_CT, pt.size = 2, features = gene_ids,order = T,raster = T, cols = c("grey",rev(viridis_pal(option = "viridis")(12))), repel=T)
gg_Fig <- lapply( 1:length(gene_ids), function(x) { gg_Fig[[x]] + labs(title=gene_names[x]) & NoLegend() & NoAxes()})

pdf("Tail_twist_0wpa_CT_UMAP_feature_TailRegMarker.pdf",width=13,height=10)
CombinePlots( gg_Fig )
dev.off()

#low quality cells cluster separate 
#c4 shows still macrophage signal
#c5 low count and no specific markers

Tail_twist_0wpa_CT = subset(Tail_twist_0wpa_CT, idents = c(0,1,2,3,7,8))


#Recluster cells to get a clean population
Tail_twist_0wpa_CT<- FindNeighbors(Tail_twist_0wpa_CT, dims = 1:50)
Tail_twist_0wpa_CT <- FindClusters(Tail_twist_0wpa_CT, resolution = 0.8)

#run UMAP
Tail_twist_0wpa_CT = RunUMAP(Tail_twist_0wpa_CT,dims = 1:50,min.dist = 0.001)

#plot result
#DimPlot(object, dims = c(1, 2), cells = NULL, cols = NULL,  pt.size = NULL, reduction = NULL, group.by = NULL,  split.by = NULL, shape.by = NULL, order = NULL, label = FALSE,  label.size = 4, repel = FALSE, cells.highlight = NULL,  cols.highlight = "red", sizes.highlight = 1, na.value = "grey50",  combine = TRUE)

pdf("Tail_twist_0wpa_CT_UMAP_PC50_res0.8.pdf",width=10,height=10)
DimPlot(object = Tail_twist_0wpa_CT, reduction = 'umap', shuffle = T, pt.size = 2)
FeaturePlot(Tail_twist_0wpa_CT, pt.size = 2, features = c("nCount_RNA","G2M.Score","eGFP","mCherry"),order = T,raster = T, cols = c("grey",rev(viridis_pal(option = "viridis")(12))))
dev.off()

#no contamination clusters identified anymore

plan("multiprocess", workers = 8)
library(tidyverse)

markers <- FindAllMarkers(Tail_twist_0wpa_CT, only.pos = TRUE,  logfc.threshold = 0.3)
markers.anno = markers
markers.anno = merge(markers.anno,anno, by.x="gene" , by.y="V1")
markers.anno$ID = markers.anno$gene

#markers.anno = markers.anno[order(as.numeric(markers.anno$cluster)),]
markers.anno = markers.anno  %>% arrange(cluster , desc(avg_log2FC))

write.csv(markers.anno,"Tail_twist_0wpa_CT_allMarker.csv")


gene_ids = c("AMEX60DD018450","AMEX60DD034707","AMEX60DD052891","AMEX60DD033766","AMEX60DD021249","AMEX60DD027155","AMEX60DD009987","AMEX60DD022442","AMEX60DD040818","AMEX60DD037674","AMEX60DD052322","AMEX60DD007644","AMEX60DD055512","AMEX60DD029436","AMEX60DD031236","AMEX60DD002658","AMEX60DD037123","AMEX60DD036008","AMEX60DD004178","AMEX60DD048972","AMEX60DD029426","AMEX60DD007033","AMEX60DD009952","AMEX60DD023726","AMEX60DD034517","AMEX60DD043904","AMEX60DD009968","AMEX60DD038105","AMEX60DD027586","AMEX60DD054775")
	
gene_names =c("PRRX1","RSPO3","FGF8","TBX18","UNCX","TCF15","MEOX1","MEOX2","SCX","TNMD","PAX7","MYF5","TWIST2","TWIST3","SOX9","OTOS","CHRDL1","PKDCC","ACAN","CNMD","COL2A1","FAM180A","DLX3","WNT5A","DLL1","SPP1","PHOSPHO1","INHBA","SULF2","CALYMMIN")



gg_Fig <- FeaturePlot(Tail_twist_0wpa_CT, pt.size = 0.2, features = gene_ids,order = T, cols = c("grey",rev(viridis_pal(option = "viridis")(12))), repel=T)
gg_Fig <- lapply( 1:length(gene_ids), function(x) { gg_Fig[[x]] + labs(title=gene_names[x]) & NoLegend() & NoAxes()})

pdf("Tail_twist_0wpa_CT_UMAP_feature_ABMarker.pdf",width=13,height=10)
CombinePlots( gg_Fig )
dev.off()


gene_ids = c("AMEX60DD034517","AMEX60DD021181","AMEX60DD021249","AMEX60DD018450","AMEX60DD034707","AMEX60DD052891","AMEX60DD033766","AMEX60DD027155","AMEX60DD009987","AMEX60DD022442","AMEX60DD040818","AMEX60DD037674","AMEX60DD007644","AMEX60DD052322","AMEX60DD055512","AMEX60DD029436","AMEX60DD054625","AMEX60DD007033","AMEX60DD018705","AMEX60DD024616","AMEX60DD038300","AMEX60DD012132","AMEX60DD031236","AMEX60DD002658","AMEX60DD037123","AMEX60DD036008","AMEX60DD004178","AMEX60DD048972","AMEX60DD029426","AMEX60DD005459","AMEX60DD043904","AMEX60DD049488","AMEX60DD033105","AMEX60DD038318","AMEX60DD031842","AMEX60DD047873","AMEX60DD034687","AMEX60DD008143","AMEX60DD048840","AMEX60DD043904","AMEX60DD009968")
gene_names =c("DLL1","LFNG","UNCX","PRRX1","RSPO3","FGF8","TBX18","TCF15","MEOX1","MEOX2","SCX","TNMD","MYF5","PAX7","TWIST2","TWIST3","TBX2","FAM180A","F13B","LTBP4","F13A1","GREM1","SOX9","OTOS","CHRDL1","PKDCC","ACAN","CNMD","COL2A1","MATN1","SPP1","MMP13","MATN3","DSP","COL5A3","COL4A1","LAMA2","ITIH5","KLF5","SPP1","PHOSPHO1")
	

gg_Fig <- FeaturePlot(Tail_twist_0wpa_CT, pt.size = 2, features = gene_ids,order = T,raster = T, cols = c("grey",rev(viridis_pal(option = "viridis")(12))), repel=T)
gg_Fig <- lapply( 1:length(gene_ids), function(x) { gg_Fig[[x]] + labs(title=gene_names[x]) & NoLegend() & NoAxes()})

pdf("Tail_twist_0wpa_CT_UMAP_feature_TailRegMarker.pdf",width=13,height=10)
CombinePlots( gg_Fig )
dev.off()

saveRDS(Tail_twist_0wpa_CT, file = "Tail_twist_0wpa_CT_SeuratObj.RDS")

```

##Run Velocity
```{r}

Tail_twist_0wpa_spliced <- Read10X(data.dir = "/mnt/SingleCellGenomics/scg_projects/10xGenomics/HLFYTDRXX_R9843/count_123454_0dpa_twist3_Full_Solo.out/Velocyto/raw/spliced")
Tail_twist_0wpa_spliced = Tail_twist_0wpa_spliced[rownames(anno), ,drop = FALSE]
Tail_twist_0wpa_spliced <- CreateSeuratObject(counts = Tail_twist_0wpa_spliced, project = "Tail_twist_0wpa_spliced", min.cells = 1, min.features = 1)

Tail_twist_0wpa_unspliced <- Read10X(data.dir = "/mnt/SingleCellGenomics/scg_projects/10xGenomics/HLFYTDRXX_R9843/count_123454_0dpa_twist3_Full_Solo.out/Velocyto/raw/unspliced")
Tail_twist_0wpa_unspliced = Tail_twist_0wpa_unspliced[rownames(anno), ,drop = FALSE]
Tail_twist_0wpa_unspliced <- CreateSeuratObject(counts = Tail_twist_0wpa_unspliced, project = "Tail_twist_0wpa_unspliced", min.cells = 1, min.features = 1)

Tail_twist_0wpa_spliced = subset(Tail_twist_0wpa_spliced, cells = colnames(Tail_twist_0wpa))
Tail_twist_0wpa_unspliced = subset(Tail_twist_0wpa_unspliced, cells = colnames(Tail_twist_0wpa))

#Velocity

library(velocyto.R)

Tail_twist_0wpa_CT_spliced = subset(Tail_twist_0wpa_spliced,cells = colnames(Tail_twist_0wpa_CT))
Tail_twist_0wpa_CT_unspliced = subset(Tail_twist_0wpa_unspliced,cells = colnames(Tail_twist_0wpa_CT))


emat <- GetAssayData(Tail_twist_0wpa_CT_spliced, slot = "counts")
nmat <- GetAssayData(Tail_twist_0wpa_CT_unspliced, slot = "counts")

# take cluster labels
cluster.label <- Tail_twist_0wpa_CT@meta.data$seurat_cluster
names(cluster.label) = colnames(Tail_twist_0wpa_CT)

gg_color_hue <- function(n) {
  hues = seq(15, 375, length = n + 1)
  hcl(h = hues, l = 65, c = 100)[1:n]
}

cell.colors = gg_color_hue(length(unique(Tail_twist_0wpa_CT@meta.data$seurat_cluster)))
#cell.colors <-  colorRampPalette(brewer.pal(12,"Set1"))(length(unique(BLct_CSDct_filter@meta.data$orig.ident)))

names(cell.colors) <- unique(cluster.label)

cell.cols <- cell.colors[cluster.label]
names(cell.cols) = colnames(Tail_twist_0wpa_CT)

# take embedding
emb <- Embeddings(Tail_twist_0wpa_CT, "umap")

# filter genes
emat <- filter.genes.by.cluster.expression(emat,cluster.label,min.max.cluster.average = 0.5)
nmat <- filter.genes.by.cluster.expression(nmat,cluster.label,min.max.cluster.average = 0.05)

length(intersect(rownames(emat),rownames(emat)))

#Estimate RNA velocity (using gene-relative model with k=20 cell kNN pooling and using top/bottom 2% quantiles for gamma fit):

fit.quantile <- 0.2
rvel.cd <- gene.relative.velocity.estimates(emat,nmat,deltaT=1,kCells=20,fit.quantile=fit.quantile)
#cell.dist=cell.dist,

#Visualize velocity on the t-SNE embedding, using velocity vector fields:
pdf("Tail_twist_0wpa_CT_UMAP_Velocity.pdf",width=10,height=10)
show.velocity.on.embedding.cor(emb,rvel.cd,n=400,scale='sqrt',cell.colors=cell.cols,cex=0.8,arrow.scale=1,show.grid.flow=TRUE,min.grid.cell.mass=0.1,grid.n=50,do.par=F,n.cores=50,cell.border.alpha = 0)
dev.off()

#Zhisong example
#show.velocity.on.embedding.cor(spring.coor,rvel.cd,n=200,scale='sqrt',cell.colors=cell.cols,cex=2,arrow.scale=1000,show.grid.flow=TRUE,min.grid.cell.mass=0.1,grid.n=80,do.par=T,cell.border.alpha = 0.1,n.cores=25, arrow.lwd = 2, bty="n", xaxt="n", yaxt="n")




```


